{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
Subsection on censorship.

{\color {red} what we want to contribute to the research community.}

>>>>

\indent \indent Censorship and other information controls
are widespread on the Internet and increasing in prevalence.
Since 2011, Freedom House has published a yearly report
on the state of Internet freedom in dozens of countries.
The 2014 report~\cite{freedom-on-the-net-2014} observes
an overall decrease in freedom worldwide,
with 36 of 65 surveyed countries decreasing in their freedom rating
since 2013 (only 12 countries had an increase).

To escape restrictive networks and communicate more freely,
users turn to a variety of censorship circumvention technologies.
What tools are necessary depends greatly on the specifics of
a particular censor;
they range from simple one-hop proxies and VPNs
to complicated steganographic systems.
Our goal is the development of an experiment
to test the usability of such tools.
We focus on one particular system,
Tor Browser, which bundles a variety of circumvention
tools designed for different use cases.
